Extreme Value Chapter 3

### 2022-03-03 Ch3_samplesize/Figures_Ch3.Rmd
Mixtures figure is done

@@

```{r fig.width=4, fig.height=5}
# Scenarios:
pis <- c( 0.1, 0.2, 0.3, 0.4)
dens_cols <- pal_mixture

# SAME SD INCREASING MEAN ------------------------------
desired_means <- c(30, 40, 50, 60)
desired_sds <- c(25, 25, 25, 25)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

# SAME MEAN INCREASING SD ------------------------------
desired_means <- c(30, 30, 30, 30)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

@@

# INCREASING SD INCREASING MEAN ------------------------------
desired_means <- c(30, 40, 50, 60)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A3 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

# DECREASING BOTH ------------------------------
desired_means <- c(60, 50, 40, 30)
desired_sds <- c(50, 40, 30, 20)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

#INCREASING MEANS DECRESING SD --------------------------------------
desired_means <- c(30, 35, 40, 50)
desired_sds <- c(50, 40, 35, 30)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A5 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
ggsave("Ch3_samplesize/Figures/Many_mixtures.png")
```

>>>>

bias_bxplot_fx <- function(data){
  data %>% 
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  # facet_wrap(~labelsamp, nrow = 1) +
  geom_boxplot() +
  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = " ") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none")
}

@@

```{r fig.width=10, fig.height=5}
# Scenarios:
pis <- c( 0.1, 0.2, 0.3, 0.4)
dens_cols <- pal_mixture

# SAME SD INCREASING MEAN ------------------------------
dir_scenario <- "ain1_samesd_upmean"

desired_means <- c(30, 40, 50, 60)
desired_sds <- c(25, 25, 25, 25)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
B1 <- bias_bxplot_fx(allin1df)

# SAME MEAN INCREASING SD ------------------------------

dir_scenario <- "ain1_samemean_upsd"

desired_means <- c(30, 30, 30, 30)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

@@

load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
B2 <- bias_bxplot_fx(allin1df)

# INCREASING SD INCREASING MEAN ------------------------------
dir_scenario <- "ain1_upsd_upmean"

desired_means <- c(30, 40, 50, 60)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
A3 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
B3 <- bias_bxplot_fx(allin1df)

# DECREASING BOTH ------------------------------
dir_scenario <- "ain1_downsd_downmean"

desired_means <- c(60, 50, 40, 30)
desired_sds <- c(50, 40, 30, 20)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
B4 <- allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  # facet_wrap(~labelsamp, nrow = 1) +
  geom_boxplot() +
  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance level estimated") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none")

#INCREASING MEANS DECRESING SD --------------------------------------
dir_scenario <- "ain1_upmean_downsd"

desired_means <- c(30, 35, 40, 50)
desired_sds <- c(50, 40, 35, 30)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
A5 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
B5 <- bias_bxplot_fx(allin1df)

# PLOT ----------------------------------

nolegBs <- plot_grid(B1, B2, B3, B4, ncol = 1)
legend_Bs <- get_legend(B4+ theme(legend.position = "right")) 
Bs <- plot_grid(nolegBs, legend_Bs, ncol = 2, rel_widths = c(1, 0.2))

As <- plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)

plot_grid(As, Bs, ncol = 2, rel_widths = c(1, 1.5))

ggsave("Ch3_samplesize/Figures/Many_mixtures.png")
```
```{r}
Bs
```
